---
title: "forest-food"
author: "Felipe Melo & Lucas Alencar"
date: '2022-09-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library####
library(readxl)
library(dplyr)
library(ggplot2)
library(geobr)
library(ggthemes)
library(ggsignif)
library(sf)
library(pracma)
library(cowplot)
library(factoextra)
library(ggfortify)
library(spdep)
library(tidyverse)
#setwd("~/Google Drive/github/forest-food")
#load(".RData")
```

## Bases de dados

```{r github, echo=TRUE}
#data####
read_xlsx('./dbcap2_clean.xlsx')-> dbcap2_clean #read to R the .xlsx file with all variables

```

## Analises PCA

```{r}
#data preparation
dbcap2_clean%>%
  select(1, ends_with(c("06","00", "08")))%>%
  glimpse()-> dbcap2_06.2
#Aalises PCA
prcomp(dbcap2_06.2[,-c(1,2)],scale. = T, center = T)->pca_06.2
summary(pca_06.2)
pca_06.2$sdev
pca_06.2$rotation
ncomp_06.2<-12
pca.varimax_06.2 <- varimax(pca_06.2$rotation[, 1:ncomp_06.2])
pca.varimax_06.2$loadings 
str(pca.varimax_06.2$loadings)
rot_load_06.2<- data.frame(matrix(as.numeric(pca.varimax_06.2$loadings), attributes(pca.varimax_06.2$loadings)$dim, dimnames=attributes(pca.varimax_06.2$loadings)$dimnames))
rawLoadings_06.2<- pca_06.2$rotation[,1:ncomp_06.2] %*% diag(pca_06.2$sdev, ncomp_06.2, ncomp_06.2)
rotatedLoadings_06.2 <- varimax(rawLoadings_06.2)$loadings
invLoadings_06.2     <- t(pracma::pinv(rotatedLoadings_06.2))
scores_06.2          <- scale(dbcap2_06.2[,-c(1:2)]) %*% invLoadings_06.2
scores_06.2
mun_scores_06<-as_tibble(data.frame(dbcap2_06.2[,1], scores_06.2))
colnames(mun_scores_06)
mun_scores_06 
write.csv(mun_scores_06, "mun_scores_06.csv")

#PCA 2017####
dbcap2_clean%>%
  select(1, ends_with(c("17", "10", "15")))%>%
  glimpse()->dbcap2_17.2

prcomp(dbcap2_17.2[,-1:-2],scale. = T, center = T)->pca_17.2
summary(pca_17.2)
pca_17.2$rotation
ncomp_17.2<-12
pca.varimax_17.2 <- varimax(pca_17.2$rotation[, 1:ncomp_17.2])
pca.varimax_17.2$loadings 
str(pca.varimax_17.2$loadings)
rot_load_17.2<- data.frame(matrix(as.numeric(pca.varimax_17.2$loadings), attributes(pca.varimax_17.2$loadings)$dim,
                                  dimnames=attributes(pca.varimax_17.2$loadings)$dimnames))
rawLoadings_17.2<- pca_17.2$rotation[,1:ncomp_17.2] %*% diag(pca_17.2$sdev, ncomp_17.2, ncomp_17.2)
rotatedLoadings_17.2 <- varimax(rawLoadings_17.2)$loadings
invLoadings_17.2     <- t(pracma::pinv(rotatedLoadings_17.2))
scores_17.2          <- scale(dbcap2_17.2[,-c(1:2)]) %*% invLoadings_17.2
scores_17.2
mun_scores_17<-as_tibble(data.frame(dbcap2_17.2[,1], scores_17.2))
colnames(mun_scores_17)
mun_scores_17
write.csv(mun_scores_17, "mun_scores_17.csv")

```

## Dados para os Mapas Food-Forest

```{r}

#Data and file for maps####
#Individual dimensions of PCA and final aggregated score - 2006####
read_municipality()-> mun_caat #All "read_" function from geobr packages might take a while to load
inner_join(mun_caat, mun_scores_06, by = "code_muni") ->map_scores_06
map_scores_06 %>%
  mutate(X1= scale(X1)) %>% 
  select(X1, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X1, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim1_06
map_scores_06 %>%
  mutate(X2= scale(X2)) %>%
  dplyr::select(X2, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X2, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim2_06
map_scores_06 %>%
  mutate(X3= scale(X3*-1)) %>% #We inverted the sign of some dimension according to the contribution of the variable that composed the PC towards food security
  dplyr::select(X3, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X3, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim3_06
map_scores_06 %>%
  mutate(X4= scale(X4*-1)) %>%
  dplyr::select(X4, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X4, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim4_06
map_scores_06 %>%
  mutate(X5= scale(X5)) %>%
  dplyr::select(X5, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X5, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim5_06
map_scores_06 %>%
  mutate(X6= scale(X6*-1)) %>%
  dplyr::select(X6, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X6, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim6_06
map_scores_06 %>%
  mutate(X7= scale(X7*-1)) %>%
  dplyr::select(X7, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X7, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim7_06
map_scores_06 %>%
  mutate(X8= scale(X8*-1)) %>%
  dplyr::select(X8, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X8, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim8_06
map_scores_06 %>%
  mutate(X9= scale(X9)) %>%
  dplyr::select(X9, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X9, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim9_06
map_scores_06 %>%
  mutate(X10= scale(X10*-1)) %>%
  dplyr::select(X10, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X10, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim10_06
map_scores_06 %>%
  mutate(X11= scale(X11*-1)) %>%
  dplyr::select(X11, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X11, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim11_06
map_scores_06 %>%
  mutate(X12= scale(X12*-1)) %>%
  dplyr::select(X12, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X12, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim12_06

read_country() ->brazil 

read_state() -> uf
uf %>% 
  filter(abbrev_state %in% c("BA","SE","PE", "AL","PB","RN","CE","PI","MG"))->uf_caat

data.frame(dim1_06$X1,dim2_06$X2,dim3_06$X3,dim4_06$X4,dim5_06$X5,dim6_06$X6,dim7_06$X7,dim8_06$X8,dim9_06$X9,
           dim10_06$X10, dim11_06$X11, dim12_06$X12) -> fs_score_06
names(fs_score_06)<-c("PC1","PC2","PC3","PC4","PC5","PC6","PC7","PC8","PC9", "PC10", "PC11", "PC12")
fs_score_06$fs_score<-scale(rowSums(fs_score_06))

#Individual dimensions of PCA and final aggregated score - 2017####
inner_join(mun_caat, mun_scores_17, by = "code_muni")-> map_scores_17
map_scores_17 %>%
  mutate(X1= scale(X1*-1)) %>% 
  select(X1, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X1, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim1_17
map_scores_17 %>%
  mutate(X2= scale(X2)) %>%
  dplyr::select(X2, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X2, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim2_17
map_scores_17 %>%
  mutate(X3= scale(X3*-1)) %>%
  dplyr::select(X3, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X3, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim3_17
map_scores_17 %>%
  mutate(X4= scale(X4)) %>%
  dplyr::select(X4, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X4, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim4_17
map_scores_17 %>%
  mutate(X5= scale(X5)) %>%
  dplyr::select(X5, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X5, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim5_17
map_scores_17 %>%
  mutate(X6= scale(X6*-1)) %>%
  dplyr::select(X6, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X6, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim6_17
map_scores_17 %>%
  mutate(X7= scale(X7*-1)) %>%
  dplyr::select(X7, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X7, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim7_17
map_scores_17 %>%
  mutate(X8= scale(X8*-1)) %>%
  dplyr::select(X8, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X8, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim8_17
map_scores_17 %>%
  mutate(X9= scale(X9*-1)) %>%
  dplyr::select(X9, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X9, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim9_17
map_scores_17 %>%
  mutate(X10= scale(X10*-1)) %>%
  dplyr::select(X10, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X10, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim10_17
map_scores_17 %>%
  mutate(X11= scale(X11*-1)) %>%
  dplyr::select(X11, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X11, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim11_17
map_scores_17 %>%
  mutate(X12= scale(X12*-1)) %>%
  dplyr::select(X12, geom) %>% 
  as.data.frame() %>% 
  mutate(category=cut(X12, breaks=c(-Inf, -1.5, -0.5, 0.5, 1.5, Inf), 
                      labels=c("very low","low","middle","high", "very high")))->dim12_17

data.frame(dim1_17$X1,dim2_17$X2,dim3_17$X3,dim4_17$X4,dim5_17$X5,dim6_17$X6,dim7_17$X7,dim8_17$X8,dim9_17$X9,
           dim10_17$X10, dim11_17$X11, dim12_17$X12) -> fs_score_17
names(fs_score_17)<-c("PC1","PC2","PC3","PC4","PC5","PC6","PC7","PC8","PC9", "PC10", "PC11", "PC12")
fs_score_17$fs_score<-scale(rowSums(fs_score_17))

inner_join(mun_caat, mun_scores_06, by = "code_muni")-> map_fsc

dbcap2_clean%>%
  mutate(fcc = nvcPerc_17 - nvcPerc_06)%>%
  select(1,2,fcc)%>%
  left_join(x = ., y = map_fsc)%>%
  glimpse() ->map_fsc


data.frame(dbcap2_17.2[,1], fs_score_06$fs_score, fs_score_17$fs_score) -> fsc

fsc%>%
  rename(fs_06 = fs_score_06.fs_score, fs_17 = fs_score_17.fs_score)%>%
  mutate(fsc = fs_17 - fs_06)%>%
  glimpse()-> fsc.score

# fsc.score %>% 
#   mutate(category=cut(fsc, breaks=c(-Inf, -1.5, 0, 1.5, Inf), # mudei para 4 categorias para ficar igual ao do forest cover
#                       labels=c("High loss","Loss","Gain", "High Gain")))->fsc.score_class
fsc.score %>% 
  mutate(category=cut(fsc, breaks=c(-Inf, 0, Inf), # mudei para 4 categorias para ficar igual ao do forest cover
                      labels=c("Net Loss","Net Gain")))->fsc.score_class

inner_join(mun_caat, fsc.score_class, by = "code_muni")-> map_fsc

dbcap2_clean%>%
  mutate(fcc = nvcPerc_17 - nvcPerc_06)%>%
  select(1,2,fcc)%>%
  left_join(x = ., y = map_fsc)%>%
  glimpse() ->map_fsc

map_fsc%>%
  mutate(relation = as.factor(if_else(condition = fcc > 0 & fsc>0, true = "Gain-Gain",
                                      false = if_else(condition = fcc > 0 & fsc < 0, true = "Gain-Lose",
                                                      false = if_else(condition = fcc< 0 & fsc > 0, true = "Lose-Gain",
                                                                      false = if_else(condition = fcc<0 & fsc <0, true = "Lose-Lose",
                                                                                      false = "pizza"))))))%>%
  glimpse()-> map_fsc

map_fsc%>%
  mutate(netFor = as.factor(if_else(condition = fcc > 0, true = "Net Gain", false = "Net Loss")))%>%
  glimpse()->map_fsc

```

## Mapas Food-Forest
### Área de estudo

```{r}
caatinga<-read_biomes()
caatinga<-caatinga[2,]
  
ggplot()+
  geom_sf(data = brazil, fill = "antiquewhite1")+
  geom_sf(data = caatinga$geom, aes(fill = "transparent"))+
  #geom_sf(data = dim1_06$geom, aes(color = "grey50"), lwd = 0.5)+
  scale_fill_manual(values = "grey50", labels = "Caatinga Biome")+
  guides(fill=guide_legend(title=NULL))+
  geom_sf(data = uf, fill = "transparent")+
  scale_x_continuous(breaks = c(-70, -55, -40))+
  scale_y_continuous(breaks = c(0, -15, -30))+
  labs(x="Longitude", y="Latitude")+
  theme_bw()+
  theme(legend.position = c(0.8, 0.2))-> fig1a
  # theme(text = element_text(family = '', size = 6),
  #       panel.grid.major = element_blank(),
  #       panel.background = element_blank(),
  #       axis.title = element_blank(),
  #       legend.position = c(0.8, 0.2),
  #       legend.key.size = unit(2, "mm"),
  #       legend.text = element_text(size = 8),
  #       legend.title = element_text(size = 8)) 
fig1a
```

## Map of Forest cover change
```{r}

ggplot()+
  geom_sf(data=map_fsc$geom, aes(fill = map_fsc$fcc), lwd=0.1)+
  scale_fill_gradientn(colours =c("#D73027", "#F46D43", "#FFEDA0", "#D9EF8B", "#A6D96A", "#66BD63", "#1A9850"), name = "Change in \nforest cover (%) \n2006-2017")+
  # scale_fill_manual(values = c("#55ab3b", "#f2220f"),name="Change in \nforest cover")+
  geom_sf(data=uf_caat, fill="transparent")+
  coord_sf(xlim = c(-48, -34), ylim = c(-17.1, -3))+
  geom_text(data = uf_caat, aes(x= c(-42, -39.5,-36.5,-35.5, -34.5, -34.4, -36, -39,-42.4),
                                y = c(-16.8, -15, -11, -10, -8.5, -7, -4.7, -2.9, -5),
                                label = c("MG", "BA", "SE", "AL", "PE", "PB", "RN", "CE", "PI")),
            size = 2)+
  scale_x_continuous(breaks = c(-48, -42, -36))+
  scale_y_continuous(breaks = c(-4,-10, -16))+
  labs(x=NULL, y=NULL)+
  theme_bw()+
  theme(legend.position = c(0.85, 0.2),
        legend.background = element_blank(),
         panel.grid.major = element_blank())-> fcc.map
  # theme(text = element_text(family = '', size = 6),
  #       panel.grid.major = element_blank(),
  #       panel.background = element_blank(),
  #       axis.title = element_blank(),
  #       axis.text.x = element_blank(),
  #       axis.ticks.x = element_blank(),
  #       legend.key.size = unit(2, "mm"),
  #       legend.position = c(0.8, 0.2),
  #       legend.text = element_text(size = 8),
  #      legend.title = element_text(size = 8))
fcc.map 

```


#Map of food security change
```{r}

fsc.score_class %>% 
  mutate(fcs_perc=(fs_17/fs_06)*100)->fsc.score_class

ggplot()+
  geom_sf(data=map_fsc$geom, aes(fill =  fsc.score_class$fsc),lwd=0.1)+
  scale_fill_gradientn(colours =c("#B35806", "#E08214", "#FDB863", "#FEE0B6", "#F7F7F7", "#D8DAEB", "#B2ABD2", "#8073AC", "#542788"), name = "Change in \nFood Security Index")+
  geom_sf(data=uf_caat, fill="transparent")+
  coord_sf(xlim = c(-48, -34), ylim = c(-17.1, -3))+
  geom_text(data = uf_caat, aes(x= c(-42, -39.5,-36.5,-35.5, -34.5, -34.4, -36, -39,-42.4),
                                y = c(-16.8, -15, -11, -10, -8.5, -7, -4.7, -2.9, -5),
                                label = c("MG", "BA", "SE", "AL", "PE", "PB", "RN", "CE", "PI")),
            size = 2)+
  scale_x_continuous(breaks = c(-48, -42, -36))+
  scale_y_continuous(breaks = c(-4,-10, -16))+
  labs(x=NULL, y=NULL)+
  theme_bw()+
 theme(legend.position = c(0.85, 0.2),
        legend.background = element_blank(),
         panel.grid.major = element_blank())-> fsc.map
  # theme(text = element_text(family = '', size = 6),
  #       panel.grid.major = element_blank(),
  #       panel.background = element_blank(),
  #       axis.title = element_blank(),
  #       legend.key.size = unit(2, "mm"),
  #       legend.position = c(0.9, 0.2),
  #       legend.text = element_text(size = 8),
  #       legend.title = element_text(size = 8))
fsc.map
```


##Map of forest cover and food security relationship

```{r}

ggplot()+
  geom_sf(data=map_fsc$geom, aes(fill = map_fsc$relation), lwd=0.1)+ # chamar map_fsc$relation do script analysis_cap2.R
  # scale_fill_manual(values = c("#d7191c",  "#fdae61", "#abd9e9", "#2c7bb6"), 
  #                   name="Forest-Food\nrelationship")+
  scale_fill_manual(values =c('#018571','#80cdc1','#dfc27d','#a6611a'))+
  # scale_fill_viridis(discrete = TRUE,  direction=-1)+
  # scale_fill_manual(values =c('#f2f0f7','#cbc9e2','#9e9ac8','#6a51a3'))+
  geom_sf(data=uf_caat, fill="transparent")+
  coord_sf(xlim = c(-48, -34), ylim = c(-17.1, -3))+
  geom_text(data = uf_caat, aes(x= c(-42, -39.5,-36.5,-35.5, -34.5, -34.4, -36, -39,-42.4),
                                y = c(-16.8, -15, -11, -10, -8.5, -7, -4.7, -2.9, -5),
                                label = c("MG", "BA", "SE", "AL", "PE", "PB", "RN", "CE", "PI")),
            size = 2)+
  scale_x_continuous(breaks = c(-48, -42, -36))+
  scale_y_continuous(breaks = c(-4,-10, -16))+
  labs(size=8, fill = "Forest cover-\nFood security") +
  labs(x=NULL, y=NULL)+
  theme_bw()+
  theme(legend.position = c(0.85, 0.2),
        legend.background = element_blank(),
         panel.grid.major = element_blank())-> fcc_fsc.map
  # theme(text = element_text(family = '', size = 6),
  #       panel.grid.major = element_blank(),
  #       panel.background = element_blank(),
  #       axis.title = element_blank(),
  #       axis.text.y = element_blank(),
  #       axis.ticks.y = element_blank(),
  #       legend.key.size = unit(2, "mm"),
  #       legend.position = c(0.9, 0.2),
  #       legend.text = element_text(size = 8),
  #       legend.title = element_text(size = 8))
 
fcc_fsc.map

```

# Juntando os mapas

```{r}
ggdraw() +
  draw_plot(fcc.map, x = 0, y = .5, width = .5, height = .5) +
  draw_plot(fsc.map, x = .5, y = .5, width = .5, height = .5) +
  #draw_plot(fcc_fsc.map, x = 0, y = 0, width = 1, height = 0.5) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, 0.5), y = c(1, 1))->fig2
fig2
```

# Generalized Linear Model
## Preparando as bases

```{r}
map_fsc%>%
  inner_join(x = ., y = select(dbcap2_clean, code_muni, nvcPerc_06, nvcPerc_17))%>%
  glimpse() ->a
```

# Testes para o ano de 2006

```{r}

lm(data = a[-1,], fs_06 ~ nvcPerc_06 + I(nvcPerc_06^2)) -> glmq.fs06_fc06
summary(glmq.fs06_fc06)
summary(aov(glmq.fs06_fc06))

ggplot(a, aes(x = nvcPerc_06, y = fs_06))+
  geom_point(colour = "#003f5c", size= 3, alpha = 1/3)+
  geom_hline(yintercept =0, linetype = "dashed")+
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), lwd = 0.5, fill = "grey20", color = "black")+
   scale_y_continuous(limits = c(-6, 6))+
  theme_base()+
  theme(legend.position = "none")+
  labs(x = NULL, y = "Food security index", title = "year of 2006")+
  theme(text = element_text(family = '', size = 12),
        plot.background = element_blank(),
        plot.title = element_text(hjust = 0.5))-> fs_fc_06
fs_fc_06
```

# Teste para o ano de 2017
```{r}
#2017
glm(data = a[-1,], fs_17 ~ nvcPerc_17 + I(nvcPerc_17^2)) -> glmq.fs17_fc17
summary(glmq.fs17_fc17)

ggplot(a, aes(x = nvcPerc_17, y = fs_17))+
  geom_point(colour = "#003f5c", size= 3, alpha = 1/3)+
  geom_hline(yintercept =0, linetype = "dashed")+
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), lwd = 0.5, fill = "grey20",  color = "black")+
  scale_y_continuous(limits = c(-6, 6))+
  theme_base()+
  theme(legend.position = "none")+
  labs(x = NULL, y =NULL, title = "year of 2017")+
  theme(text = element_text(family = '', size = 12),
        plot.background = element_blank(),
        plot.title = element_text(hjust = 0.5))-> fs_fc_17
fs_fc_17

```



# Correlações espaciais
```{r }
# Spatial autocorrelation test####

read_sf("muncat_2020.shp")->mun_cat # Essa base não está lá!
a$code_muni<-as.character(a$code_muni)
inner_join(mun_cat, a[-1,], by = c("CD_MUN" = "code_muni"))-> mun_cat_data
poly2nb(mun_cat_data, queen=TRUE)-> mat_dist2
nb2listw(mat_dist2)->mat_dist_list
lm.morantest(glmq.fs06_fc06, mat_dist_list, alternative = "two.sided")
lm.morantest(glmq.fs17_fc17, mat_dist_list, alternative = "two.sided")

#Spatial autoregressive models####
library(spdep)
library(spatialreg)

errorsarlm(data = a[-1,],
          fs_06 ~ nvcPerc_06 + I(nvcPerc_06^2),
          mat_dist_list)->sem.fs06
summary(sem.fs06)
residuals(sem.fs06)->res_lm06
moran.test(res_lm06, mat_dist_list, 999)

errorsarlm(data = a[-1,],
            fs_17 ~ nvcPerc_17 + I(nvcPerc_17^2),
            listw = mat_dist_list)->sem.fs17
summary(sem.fs17)
residuals(sem.fs17)->res_lm17
moran.test(res_lm17, mat_dist_list, 999)


# For PC1

errorsarlm(data = data_reg[-1,],#sempre lebrar de tirar esse municipio do MA
          X1 ~ nvcPerc_06 + I(nvcPerc_06^2),
          mat_dist_list)->PC1.fs06
summary(PC1.fs06)
residuals(PC1.fs06)->res_PC106
moran.test(res_PC106, mat_dist_list, 999)

errorsarlm(data = data_reg[-1,],#sempre lebrar de tirar esse municipio do MA
          X1 ~ nvcPerc_17 + I(nvcPerc_17^2),
          mat_dist_list)->PC1.fs17
summary(PC1.fs17)
residuals(PC1.fs17)->res_PC117
moran.test(res_PC117, mat_dist_list, 999)

# For PC2

errorsarlm(data = data_reg[-1,],#sempre lebrar de tirar esse municipio do MA
          X2 ~ nvcPerc_06,
          mat_dist_list)->PC2.fs06
summary(PC2.fs06)
residuals(PC2.fs06)->res_PC206
moran.mc(res_PC206, mat_dist_list, 999)

errorsarlm(data = data_reg[-1,],#sempre lebrar de tirar esse municipio do MA
          X2 ~ nvcPerc_17,
          mat_dist_list)->PC2.fs17
summary(PC1.fs17)
residuals(PC1.fs17)->res_PC117
moran.mc(res_PC117, mat_dist_list, 999)


```


# Novas análises entre Forest Cover - PC1 e PC2 (em substituição aos boxplots)
```{r}
data_reg<-data.frame(mun_scores_17[,1:3],mun_scores_06[,2:3], a[,14:15] )

#2006
data_reg %>% 
  ggplot(aes(nvcPerc_06,X1))+ geom_point(colour = "#003f5c", size= 3, alpha = 1/3)+
  geom_hline(yintercept =0, linetype = "dashed")+
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), lwd = 0.5, fill = "grey20", color = "black")+
  theme_base()+
  theme(legend.position = "none")+
  labs(x = NULL, y = "Economic Poverty (PC-1)")+
  theme(text = element_text(family = '', size = 12),
        plot.background = element_blank())-> x1_06
x1_06

data_reg %>% 
  ggplot(aes(nvcPerc_06,X2))+ geom_point(colour = "#003f5c", size= 3, alpha = 1/3)+
  geom_hline(yintercept =0, linetype = "dashed")+
  stat_smooth(method = "lm", fill = "grey20", color = "black")+
  theme_base()+
  theme(legend.position = "none")+
  labs(x = "Forest cover (%)", y = "Social Inequality (PC-2)")+
  theme(text = element_text(family = '', size = 12),
        plot.background = element_blank())-> x2_06
x2_06

# 2017
data_reg %>% 
  ggplot(aes(nvcPerc_17,X1))+ geom_point(colour = "#003f5c", size= 3, alpha = 1/3)+
  geom_hline(yintercept =0, linetype = "dashed")+
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), lwd = 0.5, fill = "grey20", color = "black")+
  theme_base()+
  theme(legend.position = "none")+
  labs(x = NULL, y = NULL)+
  theme(text = element_text(family = '', size = 12),
        plot.background = element_blank())-> x1_17
x1_17

data_reg %>% 
  ggplot(aes(nvcPerc_17,X2))+ geom_point(colour = "#003f5c", size= 3, alpha = 1/3)+
  geom_hline(yintercept =0, linetype = "dashed")+
  stat_smooth(method = "lm", fill = "grey20", color = "black")+
  theme_base()+
  theme(legend.position = "none")+
  labs(x = "Forest cover (%)", y =NULL)+
  theme(text = element_text(family = '', size = 12),
        plot.background = element_blank())-> x2_17
x2_17

```

# Juntando as regressões

```{r}
plot_grid(fs_fc_06,fs_fc_17,x1_06,x1_17,x2_06,x2_17, align = "vh",labels = "AUTO",ncol = 2, nrow = 3) ->fig3
fig3
```



# Descritivas para resultados

```{r echo=FALSE}

# Forest Cover
mun_scores_06 %>% 
  mutate(code_muni=as.numeric(code_muni))->mun_scores_06

str(mun_scores_06)

str(a)

a<-inner_join(a,mun_scores_06, by="code_muni")

a %>% 
  group_by(relation) %>% 
  # summarise_at(vars(X1,X2,X3,X4), lst(mean,sd))
  ggplot(aes(relation, X2))+geom_boxplot()

a %>%  # essa é a base mais completa
  group_by(netFor) %>% 
  summarize_at(vars(netfc), lst(mean, sd))

a %>%
  select(netfc, netfs) %>% 
  filter(netfc>10) 
  
# Food Security
a %>%  # essa é a base mais completa
  group_by(netFor) %>% 
  summarize_at(vars(netfs), lst(mean, sd))


```

